---
title: 'Analysis Report'
output:
  prettydoc::html_pretty:
    theme: architect
    mathjax: null
    css: "style.css"
keep_md: true
always_allow_html: true
self_contained: true

params:
  argosDir : dummy
  sampleID : dummy
---



```{r loadData, echo=FALSE, include=FALSE}
source("load_data.R", local=knitr::knit_global())
data=load_data(params$argosDir,params$sampleID)
```





``{r loadData, echo=FALSE, include=FALSE}
# source("load_data.R", local=knitr::knit_global())
data=load_data(params$argosDir,params$sampleID)
```





```{css, echo=FALSE}
@media screen and (max-width: 600px) {
  img.img_class {
    display: none;
  }
}
```
```{r, echo=FALSE}
htmltools::img(src = "MSKCC-logo.png",
               alt = 'logo',
               class = 'img_class',
               style = 'position:absolute; top:-120px; left:0; padding:3px; max-height: 70px', 
               # width = "30%",
               heigth = "auto"
               )
```

```{r set_defaults, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = NA)
```










```{r report_info, echo=FALSE}
report_id <- "Report uuid comes here"

report_info_table <- data.frame(c("Report uuid:"),c(report_id))

kable(report_info_table, col.names = NULL) %>% 
  kable_styling( full_width = T, position = "left")%>% 
  column_spec(1, bold = T)
```




```{r data_clinical, echo=FALSE}
clinical_header_row_css<- "background-color: #8b8da3; color: #fff;"

#"html", col.names = NULL, align = 'l'
kable(data$tbl01)
# kable(tbl01, col.names = NULL) %>% kable_styling(htmltable_class = "data_clinical_table_style", full_width = T, position = "left")%>% add_header_above(c( "Data clinical:" = 4), align= "l",extra_css= clinical_header_row_css )
```

```{r summary, echo=FALSE}
kable(data$summaryTbl, col.names = NULL) %>% kable_styling(htmltable_class = "summary_table_style", full_width = T, position = "left")%>%
  column_spec(1, bold = T)
```


```{r mutations, echo=FALSE}
row_top_css <- "background-color: #63a0e1; color: #fff;"
row_middle_css <- "background-color: #87CEFA; color: #fff;"
n <- rbind(data$mafTbl,data$cnvTbl)

kable(n) %>% kable_styling(htmltable_class = "table_class", full_width = T, position = "left")%>%
  add_header_above(c( "Somatic alterations detected in this sample:" = 5), align= "l",extra_css= row_top_css )%>%
  pack_rows("Mutations", 1, nrow(data$mafTbl), label_row_css = row_middle_css)%>%
  pack_rows("Copy Number Alterations", nrow(data$mafTbl)+1, nrow(data$mafTbl)+nrow(data$cnvTbl), label_row_css = row_middle_css)
```

```{r fusions, echo=FALSE}
kable(data$fusionTbl)
```

```{r cnvs, echo=FALSE}
kable(data$cnvTblFull)
```

